---
title: "R Presentation with Plotly"
subtitle: "Data Product Course"
author: "Six_Paths"
date: "09/12/2022"
output:
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages(library("ggplot2", quietly = T))
suppressPackageStartupMessages(library("plotly", quietly = T))
suppressPackageStartupMessages(library("cowplot", quietly = T))

```


## R Markdown

#### **Summary of this presentation : **

This presentation aims to show  case of Data representation using charting
and plotting based on plotly library.


#### **Keys section of this presentation are :**


1. Summary on Used data and purpose analysis

2. Basic and Quick Stats on Data

3. Data Representations using Plotly


## Summary  : Used data and purpose analysis

Diamonds data set was used in this analysis to make some data representation using plotly.

This data was embedded into into ggplot2 package.

It is a multivariate data set which has measurements on price and some different
diamonds characteristic (carat price, color, clarity, etc.).

A full description of this data is available on wikipedia following this link
[https://ggplot2.tidyverse.org/reference/diamonds.html].


## Basic and Quick Stats on Data  
##### (Slide with R Output)
```{r diamonds_df, echo = FALSE}
diamond_df <- diamonds
summary(diamond_df)

```


## Data Representations using Plotly
##### (Slide with Plot)

```{r plot_output, echo=FALSE}
#create histogram of values for price
diamond_plot <- plot_ly(diamonds, x = ~cut, color = ~clarity) %>%
  add_histogram() %>% layout(legend = list(x = 0.1, y = 0.9),
                             title="Diamond count by Clarity and quality")

diamond_plot

```