---
title: "R Shiny App Presentation"
subtitle: "Data Product Course"
author: "Six_Paths"
date: "12/12/2022"
output:
  ioslides_presentation: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages(library("ggplot2", quietly = T))
suppressPackageStartupMessages(library("plotly", quietly = T))
suppressPackageStartupMessages(library("cowplot", quietly = T))

### Load library
library(reshape2) 
library(plotly)

###
N_Eq<-10 # Number of equities
t <- 1000
mu <- 0.05
sigma <- 0.2
S0 <- 100

gbm_loop <- function(N_Eq = 100, t = 25, mu = 0, sigma = 0.1, S0 = 100, dt = 1./365) {
  gbm <- matrix(ncol = N_Eq, nrow = t)
  for (simu in 1:N_Eq) { gbm[1, simu] <- S0
  for (day in 2:t) {epsilon <- rnorm(1)
  dt = 1 / 365
  gbm[day, simu] <- gbm[(day-1), simu] * exp((mu - sigma * sigma / 2) 
                                             * dt + sigma * epsilon * sqrt(dt))}}
  return(gbm)}

## generate portfolio
df_eq <- gbm_loop(N_Eq, t, mu, sigma, S0)

## Set portfolio weight (Equal weighted portfolio in this example)
pf_eq_w <- rep(1/dim(df_eq)[2],dim(df_eq)[2])

## Compute continuously compounded return of assets 
df_eq_return <- diff(log(df_eq), lag=1)

## Set Colors for graph
cols = rainbow(N_Eq)
df_eq_plotly <- as.data.frame(df_eq)
names(df_eq_plotly) <- paste0("Asset_ID_", 1:dim(df_eq_plotly)[2])

df_eq_plotly$x_col <- (1:dim(df_eq_plotly)[1])
df_eq_plotly_melt <- melt(df_eq_plotly, id = "x_col") 

df_eq_graph <- plot_ly(df_eq_plotly_melt, x=~x_col, y=~value, group=~variable, color=~variable, 
                       mode = "lines") %>% layout(title = 'Dynamic of Brownian Asset price', 
                                                  xaxis = list(title = 'Nb_Simul'), 
                                                  font=t, plot_bgcolor = "#e5ecf6", 
                                                  yaxis = list(title = 'Asset_Price'), 
                                                  legend = list(title=list(text='Asset_ID')))

```


## R Markdown

#### **Summary of this presentation : **

This presentation aims to present a built and deployed Shiny application on  Rstudio's servers.

Using a reproducible pitch presentation about the application wil be describe in next pages

#### **Keys section of this presentation are :**

1. Used data and purpose analysis

2. Quick presentation of models and parameters

3. Indicators computing and Data Representations

Final App can bes acces here [https://github.com/SixChemins/R_Data_Product/tree/main/Shiny_App] 

## Summary  : Used data and purpose analysis

From Brownian asset prices, a basic equal weighted portfolio was built and associated indicators are computed 

Asset price are randomly generate using geometric Brownian motion that is a continuous-time stochastic process in which the logarithm of the randomly varying quantity follows a Brownian motion (also called a Wiener process.

For more details, please refer to follow links:
1.[https://en.wikipedia.org/wiki/Geometric_Brownian_motion]
2.[https://www.quora.com/What-is-Brownian-motion-and-how-is-it-applied-to-financial-markets]

Using generated data, an equal-weighted portfolio is built and indicators of return and variance are derived on said portfolio

## Quick presentation of models and parameters

Geometric Brownian motion vector simulate in datset used required parameters (some of them are set as tuning parameter for user)

* **So** : Start value of asset price (set at 100) 
* **mu** : Drift, mean of Brownian motion
* **Sigma** : Volatility of Brownian motion
* **N_Eq** : Number of Asset (Used in portfolio)
* **t** : Number of points for observed price (set)

Portfolio construction is done by using equal weight which means that for N asset the individual percentage is  (1/N). Note that the number of asset is also a parameter that can be tuned by user.

## Indicators computing and Data Representations (1/2)

```{r ptf_indicators, echo = TRUE}
## Compute Portfolio Return
  ptf_returns <- sum(df_eq_return * pf_eq_w)
  print(paste0("Portfolio Return is : ", 
               round(100*ptf_returns, 2), "%"))
## Compute Portfolio Volatility
  df_eq_cov <- cov(df_eq_return)
  ptf_volatility <- sqrt(t(pf_eq_w) %*% df_eq_cov %*% pf_eq_w)
  print(paste0("Portfolio Volatility is : ", 
               round(100*ptf_volatility, 2), "%"))
```


## Indicators computing and Data Representations (2/2)
```{r App_plot, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
#create histogram of values for price
df_eq_graph

```

